### 2018-07-13 latex/header.tex
removed alternative title, changed title

\noindent
{\huge\sffamily\bfseries NamPRT and NNMT – key drivers of NAD-dependent signalling \par}

\vspace{15mm}

\noindent
\textit{Alternative title:} Functional interdependencies as driving force for the evolution of NAD-dependent signalling and biosynthesis

>>>>

\noindent
{\huge\sffamily\bfseries NamPRT and NNMT – evolutionary and kinetic drivers of NAD-dependent signalling \par}
